
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}

\titleformat{\section}{\large\bfseries}{}{0em}{}
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[ -- ]
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  pdfauthor={Adam Pippert},
  pdftitle={Resume - Adam Pippert}
}

\begin{document}

\begin{center}
    \textbf{\LARGE Adam Pippert} \\
    (503) 840-2152 · \href{mailto:adam.pippert@gmail.com}{adam.pippert@gmail.com} · 
    \href{https://www.linkedin.com/in/adam-pippert}{linkedin.com/in/adam-pippert} · Beaverton, OR
\end{center}

\section*{Professional Summary}
Strategic and technically fluent Principal Solutions Architect with 15+ years of experience in enterprise automation, cloud infrastructure, and open-source technologies. Proven leader in architecting scalable solutions for telecom and enterprise customers, driving over \$6.5M in new business across major North American carriers. Promoted to Principal for cross-regional technical leadership and influence on Red Hat product strategy. Known for security-first automation design and mentoring next-generation architects.

\section*{Core Competencies}
\textbf{Technical Skills:} Ansible Automation Platform, OpenShift, RHEL, IaC, GitOps, Kubernetes, Containers, CI/CD, Security Automation

\textbf{Leadership \& Strategy:} Automation Strategy, Cross-functional Enablement, Executive Engagement, GTM Strategy, Technical Mentorship

\textbf{Tools \& Platforms:} Red Hat AI Portfolio, Git, JIRA, Google Workspace, VS Code

\section*{Professional Experience}

\subsection{Principal Specialist Solution Architect – Ansible, Red Hat}
\textit{North America Telco, TME} \hfill Jan 2023 – Present
\begin{itemize}[leftmargin=*]
    \item Led \$1.5–2M ESA deal with a major US cellular carrier via standardized Ansible NFV automation.
    \item Delivered remediation automation for another major US cellular carrier, preventing \$100M+ in compliance risk.
    \item Conducted 17+ Ansible workshops across North America, custom hybrid labs included.
    \item Integrated Ansible, ACM, OpenShift across merged telecom infrastructure to maintain service excellence.
    \item Acted as BU liaison, influencing roadmap scalability features; mentored regional SA talent.
\end{itemize}

\subsection{Associate Principal Specialist SA – Ansible \& OpenShift, Red Hat}
\hfill 2021 – 2023
\begin{itemize}[leftmargin=*]
    \item Replaced national Ansible SSA coverage, developing security and AI/ML automation messaging.
    \item Generated \$1.3M in pipeline from TME Automation Day (87+ attendees, 3-hour technical track).
    \item Enabled compliance overhaul for a large US wireline provider, averting \$25M–100M in fines.
    \item Advocated Ansible BU database improvements for telco-scale deployments; supported AAP 2.x migrations.
\end{itemize}

\subsection{Senior Specialist Solutions Architect – Storage \& OpenShift (Telco), Red Hat}
\hfill 2020 – 2021
\begin{itemize}[leftmargin=*]
    \item Led OpenShift and ACM workshops for Tier-1 telecoms; awarded Q3 CY21 SSA of the Quarter.
\end{itemize}

\subsection{Senior Account Solutions Architect – Pacific NW Enterprise, Red Hat}
\hfill 2018 – 2020
\begin{itemize}[leftmargin=*]
    \item Cloud modernization lead for Northwest enterprise accounts; won SSA of the Half, 1H CY20.
\end{itemize}

\subsection{Systems Engineer (Pre-Sales), EMC / Dell EMC}
\hfill 2016 – 2018
\begin{itemize}[leftmargin=*]
    \item Delivered modernization solutions across Northwest enterprise sector.
\end{itemize}

\subsection{Technical Marketing Engineer, Intel Corporation}
\hfill 2012 – 2016
\begin{itemize}[leftmargin=*]
    \item Produced top-rated SKO content (2015); known for clear, concise technical enablement.
\end{itemize}

\subsection{Freelance Tech \& Startups}
\hfill 2003 – 2012
\begin{itemize}[leftmargin=*]
    \item Built and failed multiple startups; engaged in DevOps learning and IT contract support.
\end{itemize}

\section*{Education}
\textbf{Bachelor of Science in Computer Science} \\
Oregon State University, Corvallis, OR

\textbf{Bachelor of Arts in Music} \\
Roanoke College, Salem, VA

\section*{Awards \& Recognition}
\begin{itemize}[leftmargin=*]
    \item Promoted to Principal Solutions Architect, Red Hat (2023)
    \item SSA of the Quarter – Q1 CY22 and Q3 CY21
    \item SSA of the Half – 1H CY20
    \item Intel SKO – Top Content Feedback Award (2015)
\end{itemize}

\section*{Certifications}
Red Hat Certified Specialist in Ansible Automation \\
Kubernetes Fundamentals (suggested) \\
[List others if held, e.g., AWS, CKA]

\section*{Customer Impact Snapshot}
\begin{itemize}[leftmargin=*]
    \item Generated \$6.5M+ in new automation business.
    \item Averted \$100M+ in fines at a large US wireline provider.
    \item Delivered automation maturity for multiple major telecom providers.
    \item Led engagements across 5 time zones, 7 Canadian provinces, 3 US states.
\end{itemize}

\end{document}
